\textls[-0]{\thetitle}

### 2023-03-18 cc-condensed.tex
Fix typo.
Change Back the Rule Name.
a comment
Update cc-condense.

\noindent
Consistency says that the type $\bot$ is not inhabited.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.

\cref{thm:consistency} is a consequence of a meta\-circular interpretation of all
the well-formedness rules, which, in particular, interprets $\bot$ in
\TT as an uninhabited type in the meta\-language.
The construction of this interpretation follows the standard model of
\citet{altkap2016}, extending it to handle linkages.
A linkage~$\LkgAdd{\lkg}{t}$ can be interpreted into a non-dependent pair where the
second component is a dependent function (modeling late binding),
%\EDJ{Suggesting changing to ``can be interpreted into non-dependent pair with dependent function for late-binding''}
as rule \ruleref{l/add} indicates.
%
We refer the reader to a supplemental file in Agda syntax for the complete proof.

@@

We prove \cref{thm:canonicity} by constructing a logical-relations model
for the well-formedness rules, following prior approaches~\cite{coquand2018canonicity,sterling2019algebraic,kaposi2019gluing}.
In particular, a closed, well formed type $\goodType{\cdot}{T}{}$ is interpreted
into a logical predicate on closed terms: the predicate includes all
closed, ``reducible'' terms of type~$T$.
%\EDJ{I will add a quote around reducible here. it is my bad to introduce "reducible" without defining it first. But my intension is to give a feeling of the dynamic operational semantic for the reader (of course OS is not here in our setting)}\YZreply{Is there a more accurate way to say things here?}\EDJreply{Because in the operational semantic, using ``reducible'' is totally fine. But in declarative style, only ``canonicity'' this word is making sense. But this ``canonicity'' is not friendly to the audience not familar with declartive style.}
The proof is available as a supplemental file in Agda syntax.

>>>>

\noindent\YZ{These paragraphs here need to be updated}
Consistency says that the type $\bot$ is not inhabited.
Thus, it is safe to use the type theory for logical reasoning, as not
every proposition is trivially provable.

@@

We prove \cref{thm:consistency} and \cref{thm:canonicity} by constructing a logical-relations model
for the well-formedness rules, following prior approaches~\cite{coquand2018canonicity,sterling2019algebraic,kaposi2019gluing}.

In particular, (1) bottom type is interpreted as an empty set in the model, making sure no syntax derivation of bottom is possible and (2) a closed, well formed type $\goodType{\cdot}{T}{}$ is interpreted
into a logical predicate on closed terms: the predicate includes all
closed, ``reducible'' terms of type~$T$, deriving boolean canonicity.
%\EDJ{I will add a quote around reducible here. it is my bad to introduce "reducible" without defining it first. But my intension is to give a feeling of the dynamic operational semantic for the reader (of course OS is not here in our setting)}\YZreply{Is there a more accurate way to say things here?}\EDJreply{Because in the operational semantic, using ``reducible'' is totally fine. But in declarative style, only ``canonicity'' this word is making sense. But this ``canonicity'' is not friendly to the audience not familar with declartive style.}
% The proof is available as a supplemental file in Agda syntax.
The proof is available in the appendix.
